---
title: "FOR 128: Midterm II"
author: "Insert Your Name Here"
format:
  pdf: default
editor: 
  mode: source
---

## Welcome

Welcome to the second midterm! This is a closed resources exam. This means course materials, past labs/quizzes, internet or AI tools, etc. are not allowed. However, you are allowed one 8.5" x 11" sheet of paper with handwritten notes (double sided) and you are allowed to use RStudio's help menu / look up documentation of functions with `?function_name`. 

Please read the exam instructions below.

Good luck!

### Instructions

The exam has 5 questions, each equally weighted at 25 points, however only your top 4 questions will be counted to your final score. You can choose to not do one problem entirely, or do all 5 and I will count your top 4. Therefore, the exam is scored out of 100 points. 

For Question 3, make sure to download "islands_long.csv" from the same place you downloaded the Quarto document for the exam.

### Deliverables (i.e., what to put in the midterm drop box)

Upload your rendered PDF (`midterm_02.pdf`) **and** Quarto (`midterm_02.qmd`) document to the exam drop box. Make sure the Quarto document properly renders to PDF, but partial credit will be given even if you cannot render the PDF (-5 points for no rendered PDF).

\newpage

## Question 0

Load any packages you'll need for this midterm below. 

```{r}
library(tidyverse)
library(pdxTrees)
```


## Question 1

(a) 

```{r}

```


(b) 

```{r}

```


(c) 

```{r}

```


(d)

```{r}

```


(e) 

```{r}

```


(f)  

```{r}

```



## Question 2

(a) 

```{r}
streets <- get_pdxTrees_streets()
```


(b)  

```{r}

```

(c) 

```{r}

```

(d)

```{r}

```



## Question 3

(a) 

```{r}

```

(b) 

```{r}

```

(c)

```{r}

```



## Question 4

For this exercise, we will use data from the `pdxTrees` R package. 

```{r}
wrc <- get_pdxTrees_parks() %>%
  filter(Common_Name == "Western Redcedar")
```

(a) 

(b) 

(c) 

```{r}

```



## Question 5

For this exercise, we will use data from the `pdxTrees` R package. 

```{r}
parks <- get_pdxTrees_parks() 
```


(a)

(b) 

(c) 

```{r}

```


## Wrap up

Congratulations! You've made it to the end of the midterm. Make sure to render your final document and submit both the .pdf and .qmd file to D2L.
