---
title: "FOR 128: Midterm I"
author: "Insert Your Name Here"
date: "10/3/2024"
format:
  pdf: default
editor: 
  mode: source
---

## Welcome

Welcome to the first midterm! Answer each question to the best of your ability. Good luck!

### Instructions

The exam has 5 questions, each equally weighted at 25 points, however only your top 4 questions will be counted to your final score. You can choose to not do one problem entirely, or do all 5 and I will count your top 4. Therefore, the exam is scored out of 100 points. 

Some questions have extra credit associated with them, allowing you to receive up to 5 bonus points on those questions. 

For Question 4, make sure to download "Loblolly.csv" from the same place you downloaded the Quarto document for the exam. 

### Deliverables (i.e., what to put in the midterm drop box)

Upload your rendered PDF (`midterm_01.pdf`) **and** Quarto (`midterm_01.qmd`) document to the exam drop box. Make sure the Quarto document properly renders to PDF, but partial credit will be given even if you cannot render the PDF (-5 points for no rendered PDF).

# Question 1

(a) 


(b)


(c)


(d) 


(e) 



# Question 2

```{r}
# run this code to create the diameter vector
diameter <- c(17, 12, -6, 10, 14, NA, 14, 8, 22)
```


(a) 

```{r}

```

(b) 

```{r}

```

(c) 

```{r}

```

(d) 

```{r}

```


# Question 3

(a) 

```{r}

```

(b) 

```{r}

```

(c) 

```{r}

```


(d) 

```{r}

```


(e) 

```{r}

```


**PARTS (f) and (g) are EXTRA CREDIT/BONUS (2.5pts each)**

(f) 

```{r}

```

(g) 

```{r}

```


# Question 4

(a) 

```{r}

```

(b) 

```{r}

```


(c) 

```{r}

```


(d) 

```{r}

```

(e) 

```{r}

```


(f) 

```{r}

```


# Question 5

```{r}

```



# Wrap up

Congratulations! You've made it to the end of the midterm. Make sure to render your final document and submit both the .pdf and .qmd file to D2L.
